Verifying Demonstrations

### 2017-08-09 SystemModel.tex
Fixes so that beamerarticle modes are correct
Adds notes and questions since meeting

\section{System Model}
\label{SystemModel}

>>>>

\mode*

\section{System model}
\label{SystemModel}

\begin{frame}
\begin{question}
  What is participating in a protest?
  We need a definition.
\end{question}
\mode<presentation>{
\begin{remark}
  \begin{itemize}
    \item This depends on the unique ring/list signature schemes.
    \item I.e.\ when we can no longer guarantee uniqueness.
    \item The one setting up that signature scheme decides.
    \item We don't know how this will be done, nor by whom.
  \end{itemize}
\end{remark}
}
\end{frame}
This sort of depends on the unique ring/list signature scheme that we use.
As long as we can provide linkability between a user's proofs, we can consider 
it the same protest.
When we cannot, it must be a new protest.
So this is supposedly decided by the one setting up the unique ring/list 
signature scheme --- which we do not know yet how it will be done.

\begin{frame}
\begin{remark}
  We provide a lower bound, since there might be participants without phones.
\end{remark}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

\begin{frame}
\begin{question}
  What assumptions do we need?
\end{question}

We assume that
\begin{itemize}
  \item Everyone has a smartphone.
  \item Can use ad-hoc networks during the event.
\end{itemize}
\end{frame}

\subsection{Adversary model}

We have two types of adversaries:
\begin{frame}
\begin{itemize}
  \item Eve tries to lower the count.
  \item Eve tries to deanonymize protesters.
\end{itemize}
\end{frame}

\mode<all>\endinput

\section{Old stuff}
